Analytic choices for analyzing multidimensional behavior: Many analysts test hypotheses about human speech --- Prospective simulations

### 2021-05-10 scripts/r/simulations/simulations.Rmd
:bug: - update sims paths

```{r prior-predictive}
# run checks
meta_bm_ppred <- brm(
  eta | se(se) ~
    (1 | team),
  data = eta_tbl,
  prior = priors,
  sample_prior = "only",
  chain = 4,
  seed = my_seed,
  file = "./models/sim/meta_bm_ppred"
)

@@

```{r meta-bm}
meta_bm <- brm(
  eta | se(se) ~
    (1 | team),
  data = eta_tbl,
  prior = priors,
  chain = 4,
  seed = my_seed,
  cores = 4,
  file = "./models/sim/meta_bm"
)
```

@@

```{r predictors-bm}
predictors_bm <- brm(
  eta | se(se) ~
    pop_sdi +
    phoc_n +
    mod_n +
    mdim +
    twin +
    me(rating_mean, rating_sd) +
    me(exp_mean, exp_sd) +
    me(belf_mean, belf_sd),
  data = eta_tbl,
  prior = preds_priors,
  chain = 4,
  iter = 8000,
  control = list(adapt_delta = 0.9999, max_treedepth = 15),
  seed = my_seed,
  cores = 4,
  file = "./models/sim/predictors_bm"
)
```

>>>>

```{r prior-predictive}
# run checks
meta_bm_ppred <- brm(
  eta | se(se) ~
    (1 | team),
  data = eta_tbl,
  prior = priors,
  sample_prior = "only",
  chain = 4,
  seed = my_seed,
  file = "./models/sims/meta_bm_ppred"
)

@@

```{r meta-bm}
meta_bm <- brm(
  eta | se(se) ~
    (1 | team),
  data = eta_tbl,
  prior = priors,
  chain = 4,
  seed = my_seed,
  cores = 4,
  file = "./models/sims/meta_bm"
)
```

@@

```{r predictors-bm}
predictors_bm <- brm(
  eta | se(se) ~
    pop_sdi +
    phoc_n +
    mod_n +
    mdim +
    twin +
    me(rating_mean, rating_sd) +
    me(exp_mean, exp_sd) +
    me(belf_mean, belf_sd),
  data = eta_tbl,
  prior = preds_priors,
  chain = 4,
  iter = 8000,
  control = list(adapt_delta = 0.9999, max_treedepth = 15),
  seed = my_seed,
  cores = 4,
  file = "./models/sims/predictors_bm"
)
```
